---
title: "Session 4"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```


# Recap
- Hard work establishing the conceptual framework for using R succesfully.

---
# Recap 
- Functions, objects, variables.
- `readRDS`
- `mean`, `select`, `filter`.
- `group_by`, `summarize`

---
## Tooling: Scripts

- Sequences of R command that accomplish a specific task.

- They are the best way to save your work for later (or someone else).

---
## Tooling: Projects

- RStudio feature to help you to organize multiple files (scripts, data, output files).

